An analysis of PCA image reconstruction for classification

### 2010-04-26 paper/paper.tex
Figuras adicionadas.
Ainda falta ajustar o texto e as referências às figuras.
Falta também retirar a menção à imagem que mostra as reconstruções (sem espaço para ela).

% TODO Figure with three ROC curves. (Legend should cointain AUCs)
% It is surprising to see that the classifier from negative PCs even has a better performance than the classifier from positive PCs.

@@

% TODO Figure with distributions from positive and negative samples

@@

% TODO Figure with three ROC curves. (Legend should cointain AUCs)

@@

% TODO Figure with distributions from grayscale and edges

\begin{table}
  \caption{Comparison of area under the curve (AUC) of the classifiers based on grayscale error, edge error, and total error, respectively, for many values of $k$. The AUCs of the edge-based classifier are always larger then the grayscale-based classifier. This indicates edge errors are more relevant to the classification.}
  \begin{center}
    \begin{tabular}{  c | c  c  c  }
      \hline
      $k$ & Gray & Edge & Total \\
      \hline
      400 & 0.9611 & 0.9863 & 0.9744 \\
      300 & 0.9694 & 0.9877 & 0.9826 \\ 
      200 & 0.9768 & 0.9905 & 0.9877 \\
      100 & 0.9851 & 0.9944 & 0.9948 \\
      50  & 0.9905 & 0.9956 & 0.9972 \\
      25  & 0.9929 & 0.9913 & 0.9984 \\
      \hline  
    \end{tabular}
  \end{center}
  \label{table-gray-vs-edge}
\end{table}

% What reference use to GA?
These findings also point out that, among all the four reconstruction errors, some are more relevant to the classification than others. However, on the total reconstruction error (equation \ref{total_error}) each error contributes equally. So, we use the weighted total reconstruction error (equation \ref{weighted_total_error}) to improve the classification accuracy. The problem with using weights is how to choose them. We can try some values and make adjusts manually, test after test. But we can also employ an optimization algorithm that looks for the values in an automated way. In this work, we use a genetic algorithm \cite{ga}. It initially chooses a set of random values and uses operations as crossover, mutation and selection to improve them during many iterations. These operations are inspired by evolutionary biology; hence the name genetic algorithms. The values are adjusted in relation to a fitness function. In our case, this functions aims to correctly classify the largest number of training samples using a given set of weights.

@@

@@

% Mover para a introdução
% It classifies based on how much a reconstruction of an image is different from the original one, that is, it classifies based on the image reconstruction error. This relies on the fact that PCA aims to minimize the least mean square error for a given set of samples and therefore the reconstruction errors for images similar to the samples are lesser than the reconstruction errors for dissimilar images. So, we train the classifier by doing PCA separately for pedestrians and non-pedestrians. When an image has to be classified, we compare the reconstructions made by both sets of principal components to determine if it contains or not a pedestrian.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=3in]{roc_pos_vs_neg}
\caption{Simulation Results}
\label{roc_pos_vs_neg}
\end{figure}
% It is surprising to see that the classifier from negative PCs even has a better performance than the classifier from positive PCs.

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{dist_pos_vs_neg}
\caption{Simulation Results}
\label{dist_pos_vs_neg}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{roc_gray_vs_edge}
\caption{Simulation Results}
\label{roc_gray_vs_edge}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{dist_gray_vs_edge}
\caption{Simulation Results}
\label{dist_gray_vs_edge}
\end{figure}

\begin{table}
  \caption{Comparison of area under the curve (AUC) of the classifiers based on grayscale error, edge error, and total error, respectively, for many values of $k$. The AUCs of the edge-based classifier are always larger then the grayscale-based classifier. This indicates edge errors are more relevant to the classification.}
  \begin{center}
    \begin{tabular}{  c | c  c  c  }
      \hline
      $k$ & Gray & Edge & Total \\
      \hline
      400 & 0.9611 & 0.9863 & 0.9744 \\
      300 & 0.9694 & 0.9877 & 0.9826 \\ 
      200 & 0.9768 & 0.9905 & 0.9877 \\
      100 & 0.9851 & 0.9944 & 0.9948 \\
      50  & 0.9905 & 0.9956 & 0.9972 \\
      25  & 0.9929 & 0.9913 & 0.9984 \\
      \hline  
    \end{tabular}
  \end{center}
  \label{table_gray_vs_edge}
\end{table}

% What reference use to GA?
These findings also point out that, among all the four reconstruction errors, some are more relevant to the classification than others. However, on the total reconstruction error (equation \ref{total_error}) each error contributes equally. So, we use the weighted total reconstruction error (equation \ref{weighted_total_error}) to improve the classification accuracy. The problem with using weights is how to choose them. We can try some values and make adjusts manually, test after test. But we can also employ an optimization algorithm that looks for the values in an automated way. In this work, we use a genetic algorithm \cite{ga}. It initially chooses a set of random values and uses operations as crossover, mutation and selection to improve them during many iterations. These operations are inspired by evolutionary biology; hence the name genetic algorithms. The values are adjusted in relation to a fitness function. In our case, this functions aims to correctly classify the largest number of training samples using a given set of weights. The function can be fine-tuned in order to give more importance in finding more pedestrians despite the false detections or to minimize the number of non pedestrians classified as pedestrians.

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{chart_auc_vs_k}
\caption{Simulation Results}
\label{auc_vs_k}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3in]{dist_gray_vs_edge_weighted}
\caption{Simulation Results}
\label{dist_weighted}
\end{figure}

@@
